Flowchart of Current Algorithm

### 2009-02-02 docs/flowchart/flowchart.tex
fixed some typos, addressed more marginpars
more future considerations

\item After {\bf React State}, setting $(\rho h)_0 = {\rm{\bf Avg}}(\rho h)$ in 
plane-parallel and $(\rho h)_0 = (\rho h)_0 - {\rm{\bf Avg}}[(\rho h)_0 - (\rho h)]$ 
in spherical by making {\tt full\_rhoh0\_evolution = FALSE} by default.  This means
that {\bf Correct Base} no longer has to exist, and the intermediate states, 
$(\rho h)_0^{(1)}$ and $(\rho h)_0^{(2)}$, no longer have to exist.  
{\bf Advect Base Enthalpy} advances $(\rho h)_0^n \rightarrow (\rho h)_0^{n+1}$ directly.

@@

\item[spherical:] See Section \ref{Sec: Advect Base Spherical} for working notes.

@@

\MarginPar{what about an $\eta_{\rho h}$?}
\end{enumerate}

>>>>

\item In {\bf Step 4} and {\bf Step 8}, move {\bf Correct Base} to immediately
before {\bf Advect Base Pressure}.

\item Should we use a predictor-corrector for updating the full-state density?
In particular, after {\bf Correct Base}, do a full-state density advance and
{\bf Correct Base} again?

\item After {\bf React State}, setting $(\rho h)_0 = {\rm{\bf Avg}}(\rho h)$ in 
plane-parallel and $(\rho h)_0 = (\rho h)_0 - {\rm{\bf Avg}}[(\rho h)_0 - (\rho h)]$ 
in spherical by making {\tt full\_rhoh0\_evolution = FALSE} by default.  This means
that {\bf Correct Base} no longer has to exist, and the intermediate states, 
$(\rho h)_0^{(1)}$ and $(\rho h)_0^{(2)}$, no longer have to exist.  
{\bf Advect Base Enthalpy} advances $(\rho h)_0^n \rightarrow (\rho h)_0^{n+1}$ directly.
This also means we don't have to deal with $\eta_{\rho h}$ or a {\bf Diffuse Base}.

@@

\item[spherical:] See Section \ref{Sec:Advect Base Spherical} for working notes.

@@
